---
layout: page
title: "Weekly Sleep and Ambience"
date: "`r format(Sys.Date(),'%b %d, %Y')`"
background: "/img/SenseHat.jpg"
output:
  md_document:
    variant: gfm
    preserve_yaml: true
knit: (function(input, encoding) {
  rmarkdown::render(input,
                    encoding = "UTF-8",
                    output_dir = "../output")})
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(include = TRUE,echo=FALSE,warning = FALSE,message=FALSE)
knitr::opts_chunk$set(fig.path = "images/")


library(ggplot2)
library(dplyr)
library(rjson)
library(DBI)
library(RPostgres)
library(httr)

# Grab the data from the ambience database

source("creds.R")

queryText = paste(readLines(file.path("..","queries","ambience.sql")),collapse = "\r\n ")

con <- dbConnect(RPostgres::Postgres(),dbname=AMB_CREDS$dbname,host=AMB_CREDS$host,port=AMB_CREDS$port,user=AMB_CREDS$user,password=AMB_CREDS$password,timezone=NULL)

res <- dbSendQuery(con,queryText)
amb_dataset <- dbFetch(res)
dbDisconnect(con)

amb_dataset = amb_dataset %>% arrange(reading_dttm)

x_lower = as.POSIXct(paste0(format(min(amb_dataset$reading_dttm),"%Y-%m-%d")," 12:00"))
x_upper = as.POSIXct(paste0(format(max(amb_dataset$reading_dttm),"%Y-%m-%d")," 12:00"))
dateList = seq(as.Date(format(x_lower,"%Y-%m-%d")),as.Date(format(x_upper,"%Y-%m-%d")),by="1 day")

# put in the requests for the sleep quality scores
# need to increment dateList one day to reflect how the sleep data is recorded

dateList = dateList + 1

r <- GET(
  url = "https://api.ouraring.com/v2/usercollection/daily_sleep"
  , query = list(start_date = dateList[1], end_date = dateList[length(dateList)])
  , add_headers("Authorization" = paste0("Bearer ",readLines("token.txt")[1]))
    )
sleep_score_json = fromJSON(content(r,as="text",encoding = "UTF-8"))

r = GET(url = "https://api.ouraring.com/v2/usercollection/sleep"
    , query = list(start_date = dateList[1], end_date = dateList[length(dateList)])
    ,add_headers("Authorization" = paste0("Bearer ",readLines("token.txt")[1]))
    )
sleep_info_json = fromJSON(content(r, as="text",encoding = "UTF-8"))

# parse the score info into dataframe records
wha = lapply(
  sleep_score_json$data
  ,function(x){
    x = unlist(x,recursive=FALSE)
    data.frame(
    "day"=x$day
    ,"score"= x$score
    )}
  )
sleepScores = do.call(rbind,wha)

# parse the sleep info json into dataframe records
wha = lapply(
  sleep_info_json$data
  ,function(x){
    x = unlist(x,recursive=FALSE)
    data.frame(
    "date"=x$day
    ,"start"= x$bedtime_start
    ,"end"=x$bedtime_end
    )}
  )
bedtimes = do.call(rbind,wha)
bedtimes$start = as.POSIXct(bedtimes$start,format="%Y-%m-%dT%H:%M:%S")
bedtimes$end = as.POSIXct(bedtimes$end,format="%Y-%m-%dT%H:%M:%S")

plot_sleep_data = left_join(bedtimes,sleepScores,by=c("date" = "day"))

names(plot_sleep_data)[names(plot_sleep_data)=="score"] <- "Sleep\nScore"
```




## `r format(Sys.Date(),'%b %d, %Y')`

The images below below are the combined results of two systems:  


* the measurements that I record as part of my [ambience database](https://snyderjo.github.io/ambience/), and  
* my sleep patterns as recorded by a wearable device.  


My hope is to identify how temperature and humidity affect my sleep, and adjust them accordingly--god help if pressure affects my sleep.  

The line represents the value of the measurement in question.  The blue boxes represent the recorded sleep from beginning to end with the color representing the sleep score.  

For a more interactive and/or exploratory version of this report [click here](weeklyReport.html)

### Temperature  

```{r Temperature, echo=FALSE}
tmp_data = 
  data.frame(
    x=c(rep(median(amb_dataset$reading_dttm),2),rep(median(amb_dataset$reading_dttm)+10^5,2))
    ,y=c(min(amb_dataset$temp),max(amb_dataset$temp),max(amb_dataset$temp),min(amb_dataset$temp))
  )

p = ggplot(data = amb_dataset) +
  aes(x = reading_dttm, y = temp) +
  geom_rect(mapping=aes(xmin=start,xmax=end,ymin=-Inf,ymax=Inf,fill=`Sleep\nScore`),data=plot_sleep_data,inherit.aes = F)+
  geom_line(color = "red")+
  xlim(x_lower,x_upper) +
  labs(
    x = "reading date-time"
    ,y = "Temperature (C)") 

print(p)
```

Some of you might be asking: *Does it really get above 40 (104 degrees Fahrenheit) in your bedroom???*  
No.  The sensor is attached to a raspberry pi, which produces a good amount of heat on its own.  The above data measures temperature with a consistent bias.

### Humidity  

```{r humidity, echo=FALSE}
p = ggplot(data = amb_dataset) +  geom_rect(mapping=aes(xmin=start,xmax=end,ymin=-Inf,ymax=Inf,fill=`Sleep\nScore`),data=plot_sleep_data,inherit.aes = F)+
  aes(x = reading_dttm, y = humidity) +
  geom_line(color = "orange")+
  xlim(x_lower,x_upper) +
  labs(
    x = "reading date-time"
    ,y="Humidity (%)"
    ) +
  guides(color=guide_legend(title="Sleep\nScore"))

print(p)

```

### Pressure  

```{r pressure, echo=FALSE}
p = ggplot(data = amb_dataset) +
  aes(x = reading_dttm, y = pressure) +
  geom_rect(mapping=aes(xmin=start,xmax=end,ymin=-Inf,ymax=Inf,fill=`Sleep\nScore`),data=plot_sleep_data,inherit.aes = F)+
  geom_line(color = "green")+
  xlim(x_lower,x_upper) +
  labs(
    x = "reading date-time"
    ,y="pressure (mbar)"
    )

print(p)

```


#### A couple of notes:  

* What gives with the delay between the date this report is rendered vs. what is displayed below?  
  + If the data were immediate, it would be entirely too clear when I was out of town--information I'm not keen to share.  
* There are notable gaps in data.  Why?  
   + Some nights, I forget to put on the wearable.  
   + Some days the [DAG](https://airflow.apache.org/docs/apache-airflow/1.10.9/concepts.html) fails for no discerable reason--you might take it up with Apache.  
   + Sometimes, the device itself simply fails to record. ¯\\\\\_(ツ)\_/¯  


